mixchar

### 2018-08-12 README.Rmd
add DOI badge
correct url for website articles

@@

Below we will show a basic implementation of the package. For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/Background). You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar) or in the vignette that you can access via R by installing with the `build_vignettes` argument as follows:

>>>>

[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)

@@

Below we will show a basic implementation of the package. For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/mixchar/articles/Background.html). You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html) or in the vignette that you can access via R by installing with the `build_vignettes` argument as follows:
